\emph{Author:}
\href{http://peeragogy.org/resources/meet-the-team/}{Maria Arenas}, with
contributions by
\href{http://peeragogy.org/resources/meet-the-team/}{Charlie Danoff}

Facilitation is a process of helping groups work cooperatively and
effectively. Facilitation can be particularly helpful for individuals
who, based on a certain level of insecurity or inexperience, tend to
lurk rather than participate. At the same time, it in peeragogy, a
facilitator isn't necessarily an ``authority'': rather, facilitation
work is done in service to the group and the group dialogue and process.
For example, a facilitator may simply ``hold space'' for the group, by
setting up a meeting or a regular series of discussions.

\subsection{}

\subsection{Co-facilitating in peer-to-peer learning}

Co-facilitation can be found in collaborations between two or more
people who need each other to complete a task, for example, learn about
a given subject, author a technical report, solve a problem, or conduct
research Dr. Fink writes in \emph{Creating Significant Learning
Experiences}(Jossey Bass, 2003) that ``in this process, there has to be
some kind of change in the learner. No change, no learning''.
Significant learning requires that there be some kind of lasting change
that is important in terms of the learner's life; therefore a way to
measure the effectiveness of co-facilitation is if there's been a change
in the peer group.

\newpage
\begin{quote}
The board of a housing association needs to set a strategy that takes
account of major changes in legislation, the UK benefits system and the
availability of long term construction loans. Julian, eager to make use
of his new-found peeragogical insights suggests an approach where
individuals research specific factors and the team work together to draw
out themes and strategic options. As a start he proposes that each board
member researches an area of specific knowledge or interest. Jim, the
Chairman, identifies questions he wants to ask the Chairs of other
Housing Associations. Pamela (a lawyer) agrees to do an analysis of the
relevant legislation. Clare, the CEO, plans out a series of meetings
with the local councils in the boroughs of interest to understand their
reactions to the changes from central government. Jenny, the operations
director, starts modelling the impact on occupancy from new benefits
rules. Colin, the development director, re-purposes existing work on
options for development sites to reflect different housing mixes on each
site. Malcolm, the finance director, prepares a briefing on the new
treasury landscape and the changing positions of major lenders. Each
member of the board documents their research in a private wiki. Julian
facilitates some synchronous and asynchronous discussion to draw out
themes in each area and map across the areas of interest. Malcolm, the
FD, adapts his financial models to take different options as parameters.
Clare refines the themes into a set of strategic options for the
association, with associated financial modelling provided by Malcolm.
Individual board members explore the options asynchronously before
convening for an all-day meeting to confirm the strategy.
\end{quote}
\subsection{Which roles, competences and skills do we need to
co-facilitate?}

Co-facilitation roles can be found in groups/teams like basketball,
health, Alcoholics Anonymous, spiritual groups, etc. For example,
self-help groups are composed of people who gather to share common
problems and experiences associated with a particular problem,
condition, illness, or personal circumstance.

``Freedom to Learn'' is among the learning theories for which
\href{http://peeragogy.org/resources/literature-review-peeragogy/}{Carl
Rogers} was known. Commenting on Rogers' related work, Barrett-Lennard
remarked: ``\ldots{}he offered several hypothesized general principles.
These included: We cannot teach another person directly; we can only
facilitate his learning. The structure and organization of the self
appears to become more rigid under threat; to relax its boundaries when
completely free from threat\ldots{}. The educational situation which
most effectively promotes significant learning is one in which 1) threat
to the self of the learner is reduced a minimum, and 2) differentiated
perception of the field of experience is facilitated.''

Part of the facilitator's role is to create a safe place for learning to
take place; but they should also challenge the participants. As John
Wooden said of coaching: ``Be quick, but don't hurry.''
\href{http://en.wikipedia.org/wiki/John\_Heron}{John Heron} articulated
this aspect of facilitation well:

\begin{quote}
``Too much hierarchical control, and participants become passive and
dependent or hostile and resistant. They wane in self-direction, which
is the core of all learning. Too much cooperative guidance may
degenerate into a subtle kind of nurturing oppression, and may deny the
group the benefits of totally autonomous learning. Too much autonomy for
participants and laissez-faire on your part, and they may wallow in
ignorance, misconception, and chaos.''
\end{quote}
\subsection{Co-facilitating discussion forums}

If peers are preparing a forum discussion, here are some ideas from
``The tool box'', that can be helpful as guidelines for running this
type of meetings:

\begin{itemize}
\item
  Explain the importance of collaborative group work and make it a
  requirement.
\item
  Establish how you will communicate in the forum
\item
  Be aware of mutual blind spots in facilitating and observing others
\item
  Watch out for different rhythms of intervention''.
\end{itemize}
\subsection{Co-facilitating wiki workflows}

A good place to begin for any co-facilitators working with a wiki is
Wikipedia's famous ``5 Pillars.''

\begin{itemize}
\item
  Wikipedia is an encyclopedia
\item
  Wikipedia writes articles from a neutral point-of-view
\item
  Wikipedia is free content that anyone can edit, use, modify, and
  distribute.
\item
  Editors should interact with each other in a respectful and civil
  manner.
\item
  Wikipedia does not have firm rules.
\end{itemize}
\subsection{Co-facilitating live sessions}

Learning experiences in Live Sessions which include Social Media and co
facilitating exercise is described in the article'' Learning
Re-imagined: Participatory, Peer, Global, Online`` by Howard Rheingold,
we have taken inspiration from his points and re-mixed them slightly.

\begin{itemize}
\item
  Establish roles for co facilitators and participants (moderator,
  technical recorder, writer to take notes, etc..).
\item
  Provide a reading list -- indicating what is really important and what
  is more ``nice to know''.
\item
  Ideally before, or when the session begins, take some time to allow
  participants to familiarize themselves with the tools.
\item
  Introduce yourself and your peers (co-facilitators) and ask the
  members to make a brief introduction of themselves.
\item
  Review the agenda for the session, both to make sure there \emph{is}
  an agenda (at the start) and to make sure everything was covered (at
  the end).
\item
  Online tools like: Mumble, Diigo, Etherpad and chat can be used to
  communicate and interact in the session. However, consider whether
  participants are interested in experimenting with lots of tools. Often
  more tools (and some content) can end up making tasks harder.
\item
  Keep it Simple Stupid, or KISS: Remember you came together with your
  peers to accomplish something not to discuss an agenda or play with
  online tools; keep everything as easily accessible as possible to
  ensure you realize your peer goals.
\end{itemize}
\subsection{Paragogical Action Review}

Following any co-facilitating session it is essential that the
co-facilitators come together and review what happened. A useful
framework is the Paragogical Action Review (PAR), based on the U.S.
Army's
\href{http://www.africom.mil/WO-NCO/DownloadCenter/\%5C40Publications/Training\%20the\%20Force\%20Manual.pdf}{After
Action Review}, which has four components, to which we have added a
fifth. A further difference in the Paragogical Action Review is that it
need not take place ``after'' the action, but can be integrated into the
action (accordingly, we use a present tense phrasing).

\begin{itemize}
\item
  Review what was supposed to happen (training plans)
\item
  Establish what is happening
\item
  Determine what's right or wrong with what's happening
\item
  Determine how the task should be done differently in the future
\item
  Share your notes with your other peers for feedback and to improve
  things going forward
\end{itemize}
Here we can make use of an obvious pun: in golf, the \emph{par} is
related to the difficulty of play. If we understand the difficulties in
advance, we can help participants prepare to meet them. Additionally if
we reassess the difficulties and challenges as we go, we can adapt our
technique to suit current needs. The key to using the PAR to effectively
facilitate co-learning is replacing the ``blind spot'' at the center of
every defensive formation with a horizon, allowing our thought process a
vigorous confrontation with mystery. Instead of finding the `unknown' at
the end of a long upriver journey amidst dubious colonial and racial
politics, we find it right in the heart of our mediated communications,
in the form of silence.

\subsubsection{Resources}

\begin{enumerate}
\item
  \href{http://www.scribd.com/doc/54544925/51/TRAINING-TOPIC-Co-facilitation-skills}{Peer
  Education: Training of Trainers Manual}; UN Interagency Group on Young
  Peoples Health
\item
  \href{http://www.breakoutofthebox.com/Co-FacilitatingPfeifferJones.pdf}{Co
  Facilitating}: Advantages \& Potential Disadvantages. J. Willam
  Pfeifer and John E Johnes
\item
  A
  \href{http://reviewing.co.uk/archives/art/13\_1\_what\_do\_facilitators\_do.htm\#8\_WAYS\_OF\_FACILITATING\_ACTIVE\_LEARNING}{summary}
  of John Heron's model on role of facilitators
\item
  \href{http://www.infed.org/thinkers/et-rogers.htm}{C}\href{http://www.infed.org/thinkers/et-rogers.htm}{arl
  Rogers, Core Conditions and Education}, Encyclopedia of Informal
  Education
\item
  \href{http://www.studygs.net/peermed.htm}{Peer Mediation}, Study
  Guides and Strategies
\item
  \href{http://sk.cupe.ca/updir/cofacilitation-handouts.doc}{Co-Facilitation:
  The Advantages and Challenges}, Canadian Union of Public Employees
\item
  \href{http://community.bistudio.com/wiki/Bohemia\_Interactive\_Community:Guidelines}{Bohemia
  Interactive Community Wiki Guidelines}
\item
  Barrett-Lennard, G. T. (1998)
  \href{http://openlibrary.org/works/OL2014352W/Carl\_Rogers'\_Helping\_System}{\emph{Carl
  Roger's Helping System. Journey and Substance}}, London: Sage
\item
  \href{http://en.wikipedia.org/w/index.php?title=Wikipedia:Five\_pillars\&oldid=501472166}{5
  Pillars of Wikipedia}, from Wikipedia
\item
  \emph{\href{http://www.africom.mil/WO-NCO/DownloadCenter/\%5C40Publications/Training\%20the\%20Force\%20Manual.pdf}{Training
  the Force}, (2002)}US Army Field Manual \#FM 7-0 (FM 25-100)
\item
  \href{http://dmlcentral.net/blog/howard-rheingold/learning-reimagined-participatory-peer-global-online}{Learning
  Reimagined: Participatory, Peer, Global, Online}, by Howard Rheingold
\item
  \href{http://www.researchgate.net/}{Research Gate} is a network
  dedicated to science and research, in which members connect,
  collaborate and discover scientific publications, jobs and
  conferences.
\item
  \href{http://ctb.ku.edu/en/tablecontents/section\_1180.aspx}{Creating
  and Facilitating Peer Support Groups}, by The Community Tool Box
\item
  \href{http://www1.villanova.edu/content/villanova/artsci/vcle/resources/toolkit/\_jcr\_content/pagecontent/download\_8/file.res/FacilitationTips.doc}{Facilitation
  Tips}, by Villanova University
\item
  \href{http://pippabuchanan.com/2011/09/04/herding-passionate-cats-the-role-of-facilitator-in-a-peer-learning-process/}{Herding
  Passionate Cats: The Role of Facilitator in a Peer Learning}, by Pippa
  Buchanan
\item
  \href{http://webpages.sou.edu/~vidmar/SOARS2008/vidmar.ppt}{Reflective
  Peer Facilitation: Crafting Collaborative Self-Assessment}, by Dale
  Vidmar, Southern Oregon University Library
\item
  \href{http://www.umass.edu/ewc/ea/Facilitation\%20Skills/important\%20tips.doc}{Effective
  Co-Facilitation}, by Everywoman´s Center, University of Massachussetts
\item
  "T\href{www.ncsu.edu/park\_scholarships/pdf/chris\_argyris\_learning.pdf?}{eaching
  smart people how to learn}" by Chris Argyris, Harvard Business Review
  69.3, 1991; also published in expanded form as a
  \href{http://www.amazon.com/Teaching-People-Harvard-Business-Classics/dp/1422126005}{book}
  with the same name.
\end{enumerate}
