\begin{refsection}

% DK: I am not sure that this is a Pattern. It is a role for sure, but is it a solution to a problem? Maybe the name of the pattern is wrong. Something like Welcome Wagon? Something that evokes the response to the Newcomer.


\paragraph{Context}
% DK: This is an interesting point. I am not sure it is Context. Maybe Rationale?
When there's learning happening, it's because there is someone who is new to a topic, or to something about the topic.
\textbf{There is an `invisible hand' in peeragogy that makes it so that each person pursuing his or her own optimal course of learning is what's best for the community.  However, this does not isolate us from one another, but draws us together.}

\paragraph{Problem} Newcomers can feel overwhelmed by the amount of things to learn.  They
don't know where to start.  They may have a bunch of ideas that the
oldtimers have never considered -- or they may think they have new
ideas, which are actually a different take on an old idea; see
\patternname{Reduce, reuse, recycle}. People who are new to the project can tell you what makes their participation difficult.  Since you're learning as you go as well, you can ask yourself the same question: what aspects of this are difficult for me?  

% DK: This seems a little spare
\paragraph{Solution}
In an active learning context, we render assistance to others more effectively when we do
so as peers, rather than doing it as experts operating in a \emph{provisionist} mode
\cite{boud2005peer}.  Instead of thinking of newcomers as
``them'', and trying to provide solutions, we focus on newcomers as
``us'' -- which makes the search for solutions that much more urgent.
We permit ourselves to ask naive questions.  We entertain vague ideas.
We add concreteness by trying \patternname{A specific project}.  We may then genuinely turn
to others for help. 

% DK: I can empathize :+) I wonder if there is a pattern that is missing. Vision? A clear articulation about what the effort is for
%
\paragraph{Rationale} 
%
Sharing vulnerability and confusion gives us a chance to learn
together.  A newcomer's confusion about how best to get involved or
what the point of all this actually is may be due to a lack of
structure in the project \patternname{Roadmap}, and it points to
places where others in the project probably have something to learn too.
%
%% In the words of Antoine de Saint-Exup\'ery:
%% ``If you want to build a boat, do not instruct the men to saw wood,
%% stitch the sails, prepare the tools and organize the work,
%% but make them long for setting sail and travel to distant lands.''

% DK: The resolution should describe the circumstance after applying the solution. This seems to be describe the circumstance without the solution.
\paragraph{Resolution}
An awareness of the difficulties that newcomers face can
help us be more compassionate to ourselves and others.  We
become open to new ideas, which can show how we have
been limiting ourselves.
%
Relative to the goals of effecting real change and enhancing the
world's liveability, we really are beginners.  We will have a better chance of making
the project useful for others if we're clear about how it is useful to \emph{us}.

\paragraph{Example 1} Wikipedia \patternnameplural{Newcomer} can make use of resources that
include a ``Teahouse'' where questions are welcomed, a platform extension that changes the user
interface for new editors, and lots of documentation.\footnote{\url{https://en.wikipedia.org/wiki/Wikipedia:Teahouse}}%
\textsuperscript{,}\footnote{\url{https://en.wikipedia.org/wiki/Wikipedia:GettingStarted}}%
\textsuperscript{,}\footnote{\url{https://en.wikipedia.org/wiki/Help:Editing}}
The efforts of exceptional newcomers may be given special
recognition.\footnote{\url{https://en.wikipedia.org/wiki/Template:The_New_Editor\%27s_Barnstar}}
Newcomer ``survival'' is of interest to the Wikimedia
Foundation.\footnote{\url{https://meta.wikimedia.org/wiki/Research:Newcomer_survival_models}}
The degree to which Wikimedia projects emphasize continuous upskilling
(\`a la the \patternname{Newcomer} pattern) is somewhat less clear.

\paragraph{Example 2} It will often be pragmatic to connect
\patternnameplural{Newcomer} with employment, so that the future
university may see a closer coupling of science and industry than is
held in the former model.  Inspiration can be drawn the London-based freelancing cooperative Founders\&Coders, which is
able to offer intensive training in web development at no cost to
successful applicants, on the basis that some trainees will choose to
join the cooperative as paying members later
on.\footnote{\url{http://www.foundersandcoders.com/academy/}}


\begin{framed}
\noindent 
\emph{What's Next.}
A more detailed (but non-limiting) ``How to Get Involved'' walk-through or ``DIY Toolkit'' would be good to develop. We can start by listing some of the things we're currently learning about.
\end{framed}

\printbibliography[heading=subbibliography]
\end{refsection}
