\subsubsection{Main Actor}

A student, Madeleine, who is trying to learn multivariable calculus.

\subsubsection{Main Success Scenario}

\begin{enumerate}
\item
  Madeleine is enrolled in an advanced calculus course at university.
  She learns about PlanetMath from her instructor who recommends it as a
  place for extra practice with homework problems. Madeleine creates an
  account, fills in basic profile information, and starts solving
  problems that the system supplies based on the information she
  supplied in her profile.
\item
  The problems that the system supplies are automatically linked to
  reference resources in PlanetMath's encyclopaedia. This expository
  material gives Madeleine easy access to the relevant mathematical
  concepts, examples, and hints needed for solving the increasingly
  difficult practice problems. However, she eventually runs into a
  problem where neither the automatically supplied information, nor her
  current knowledge of the subject, is sufficient. She's completely
  stuck on a problem having to do with water flow in a pipe! Madeleine
  attaches a help request to the problem: ``I understand that I have to
  use the two variables \emph{x} and \emph{y} to solve for water flow,
  but I don't understand what the boundary limits of the equations would
  be: do I have to convert it to polar coordinates?"
\item
  This request is noticed by Natalie, a mathematics graduate student who
  regularly looks at the feed showing ``recent requests for help with
  advanced calculus.'' She sees that the reference resources linked to
  Madeleine's problem are probably not sufficient, and that Madeleine's
  idea about using polar coordinates would work. Natalie makes some
  changes to the encyclopaedia indicating that converting to converting
  to polar coordinates can be necessary in pipe flow problems, and
  sketches an example. Natalie then checks that this information links
  to Madeleine's problem correctly, and alerts Madeleine to the changes.
  With this new information, Madeleine is not only able to solve her
  problem, but can proceed with confidence: she had the right idea after
  all!
\end{enumerate}
