\begin{refsection}

\paragraph{Context} We've maintained and revised our pattern catalog over a period of years.  We're achieving
the ``What's Next'' steps attached to some of the patterns.
\textbf{We have limited energy, and therefor need to ask: where should we set the focus?}

\paragraph{Problem} Not all of the patterns we've noticed remain equally relevant.  In particular, some of the patterns no longer lead to concrete next steps.

\paragraph{Solution} In order to maintain focus, is important to ``tune'' and ``prune'' the collection of patterns receiving active attention.  Connect this understanding to concrete actions undertaken in the project by frequently asking questions like these:
\begin{quote}
(1) Review what was supposed to happen.
(2) Establish what is happening/happened.
(3) Determine what’s right and wrong with what we are doing/have done.
(4) What did we learn or change? 
(5) What else should we change going forward?  \cite[Chapter 28]{peeragogy-handbook}.
\end{quote}
%
After reviewing our activities with respect to these questions, our
current priorities will become clearer.  If a particular pattern is no
longer of current relevance, move it to a
\patternname{Scrapbook}.\footnote{\url{http://paragogy.net/Scrapbook}.}  
%
In addition to retired patterns, use the scrapbook to maintain a
backlog, or ``parking lot,'' of proto-patterns, in the form of
outstanding problems, issues, and concerns.  Don't limit yourself to
\emph{your own} creativity: include bookmarks to or clippings from
patterns from other sources (see \patternname{Reduce, reuse, recycle}).

\paragraph{Rationale} 
We want our pattern catalog to be concretely useful and actively used,
and to keep attention focused on the most relevant issues.
If a pattern is not specifically useful or actionable at the
moment, sufficient time for reflection may offer a better
understanding, or it may prove useful in a different context.

\paragraph{Resolution} 
Judicious use of the \patternname{Scrapbook} can help focus project participants, and can make it easier to communicate current priorities to others in a clear manner.  The currently active pattern catalog is leaner and more action-oriented as a result.
%
A realistic and useful focus takes both the past and the future into account.  If the \patternname{Roadmap}
shows where we're going, it is the \patternname{Scrapbook} that shows most clearly where we've been.

\paragraph{Example 1} Now that new plans are being formed, the Wikimedia Foundation's previous ``five year plan'' somewhat
resembles a \patternname{Scrapbook} \cite{wikimedia2011plan}.

\paragraph{Example 2} 
In the future university, the patterns described here will continue to
shape the landscape, but considerable activity will be focused on new
problems and new patterns -- just as a university campus grows and
changes with the addition of new buildings.

\begin{framed}
\noindent 
\emph{What's Next.}
After pruning back our pattern catalog, we want it to grow again: new patterns are needed.
One strategy would be to ``patternize'' the rest of the \emph{Peeragogy Handbook.}
\end{framed}

\printbibliography[heading=subbibliography]
\end{refsection}
