\subsection{Main Actor}

Trinity, the daughter of a Texas oil magnate.

\subsection{Soundtrack}

\href{http://www.youtube.com/watch?v=NWsX9ggfL2Q}{You Make Me Like
Charity} by The Knife

\subsection{Main success scenario}

\begin{enumerate}
\item
  Trinity has spent the last year traveling around the world to join in
  various \#Occupy protests. Her aim is to get people in the movement
  thinking about how they can empower themselves.
\item
  It's tricky though, because as much as she knows she has an impact on
  individuals, she still sees a lot of problems in the world, which,
  given her manic-depressive tendencies, she tends to find very
  disturbing.
\item
  She reaches out to other folks who are privileged in one way or
  another -- and a bunch of ``normal folks'' -- trying not only to bring
  about political change, but trying to establish a degree of personal
  friendship and camaraderie, and a feeling of ``belonging in the
  world''. For her, this is a constant struggle. She finds that working
  with other people on concrete tasks keeps her from spiraling into a
  state of gloom. In the mean time, she's also building a tremendous
  amount of knowledge about the way social movements and political
  processes work.
\end{enumerate}
\subsection{Footnote}

``The Knife is now recording a new album to be released in 2012. Lately
we have read a lot about the ongoing discrimination of Romani people in
Europe which is totally unacceptable. The forced evictions must stop and
adequate alternative housing must be arranged. Now!'' --
\href{http://theknife.net/take-action-for-the-housing-rights-of-roma-in-rome}{The
Knife}
