\documentclass[twoside]{article}


% ------
% Fonts and typesetting settings
\usepackage[sc]{mathpazo}
\usepackage[T1]{fontenc}
\linespread{1.05} % Palatino needs more space between lines
\usepackage{microtype}


% ------
% Page layout
\usepackage[hmarginratio=1:1,top=32mm,columnsep=20pt]{geometry}
\usepackage[font=it]{caption}
\usepackage{paralist}
\usepackage{multicol}

% ------
% Lettrines
\usepackage{lettrine}


% ------
% Abstract
\usepackage{abstract}
	\renewcommand{\abstractnamefont}{\normalfont\bfseries}
	\renewcommand{\abstracttextfont}{\normalfont\small\itshape}


% ------
% Titling (section/subsection)
\usepackage{titlesec}
\renewcommand\thesection{\Roman{section}}
\titleformat{\section}[block]{\large\scshape\centering}{\thesection.}{1em}{}


% ------
% Header/footer
\usepackage{fancyhdr}
	\pagestyle{fancy}
	\fancyhead{}
	\fancyfoot{}
	\fancyhead[C]{Journal Peeragogy article $\bullet$ April 2012 $\bullet$ Vol. I, No. 3}
	\fancyfoot[RO,LE]{\thepage}


% ------
% Clickable URLs (optional)
\usepackage{hyperref}

% ------
% Maketitle metadata
\title{\vspace{-15mm}%
	\fontsize{24pt}{10pt}\selectfont
	\textbf{Roadmaps in Peer Learning for Sustainable Learning
Design}}
\author{%
	\large
	\textsc{Peragogy in Action Team}\thanks{peeragogy.org \href{http://www.peeragogy,.org}{peragogy.org}} \\[2mm]
	\normalsize	Peeragogy in action\\
	\vspace{-5mm}
	}
\date{}



%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\maketitle
\thispagestyle{fancy}

\begin{abstract}
\noindent Does it do color changes?  No, too bad.
\end{abstract}
	
\begin{multicols}{2}

\section{Introduction - Purpose of the Peeragogy Project}

%% SYNCED CONTENT FROM CHARLIE'S EDIT @ April 1, 16:47 UK time

Wikipedia-like project for learning
but with a rather different orientation from Wikiversity
Analogy to the historical university (as a guild)
Differences between this, P2PU, Wikiversity, etc.

\subsection{2012 Problem Solved - Peeragogy Handbook}

$\rightarrow$ THESIS: Specifically we seek to transition from an innovative theoretical project to a sustainable, easily replicable peer project problem solving accelerator dynamically measuring assessment.

Peeragogy is replicable techniques and patterns for effective peer learning and problem solving. Without any formal institution or pay, a group of volunteer peers came together and wrote a cohesive preliminary treatise on peeragogy, far richer than what any one of these people could have produced alone.

We utilized a variety of technologies to get work done: live meetings and loose bureaucracy via team organizations and leaders of different sub-projects. To facilitate asynchronous collaboration: Social Media Classroom, Social Bookmarking, Google Docs, Google+, WordPress, LaTeX, Lulu, Twitter, Blackboard Collaborate, Git, the Creative Commons Zero Public Domain Dedication, Google Hangouts and more. Obviously each offered its own pros and cons, but peeragogy is not bound to particular digital tools nor the digital world at all. For example, a physical interpretation was taken by Anna, Paola, Gigi and Amanda who held a workshop at the Open Knowledge Conference 2013 in Helsinki.\footnote{ \url{http://okfestival.org/peeragogy-handbook-workshop/} and \url{http://www.youtube.com/watch?v=P2UJrN58MVI} leading to the peeragogy project participating in the Open Book. Also, Vanessa and Charlie collaborated to share the Handbook at the Open Education Conference 2012 in Canada as part of its Remixathon \url{http://openedconference.org/2012/happenings/remixathon-info/}}

Figure 1: Work by Amanda Lyons from \url{http://peeragogy.org/peeragogy-in-action/}

A different angle is taken from A. T. Ariyaratne's essay on Rural Self Help[7], one of the foundational writings of the Sarvodaya Shramadana movement in Sri Lanka[fn 4], begins:

Nobody needs to teach rural communities about ``group effort'' and ``self-help''. [...] The real question, therefore, is to examine what are the constraints that exist inhibiting the expression of their group effort and self-help qualities designed to improve food and nutrition levels, clothing, shelter, health, sanitation, education and cultural life?

We approach peer learning in a similar spirit: it is something we all know how to do, but can't always do well. Intuitively, there are bound to be difficulties for a group of peers studying a subject together, outside a traditional classroom or without a teacher. Indeed, peer learning is different from other forms of group effort, the proverbial ``barnraising'' for example, in which the persons involved can be presumed to know how to build barns - or at least to know someone who knows, and stand ready to take orders.

Typically, peers are not experts in learning, didactics, or in the subject they are studying, and are faced with multiple difficulties associated with putting together knowledge about the subject, assembling a suitable learning strategy, and communicating with one another.\footnote{After A.T. \ldots to here is viz from \url{http://www.paragogy.net/wiki/ParagogyPaper2}}

As of early 2013 we are translating the handbook into multiple languages, and the Italian effort is focused on the MediaWiki powered Wikibooks platform; additionally team members have experimented with the Federated Wiki for translation and other possibilities. Our hub for archival and linkage purposes remains the Social Media Classrom; thus, With each new tool however; the question of connecting back into the overall flow of work and data coherently poses new challenges and solutions are usually, but not always found.

For context all of this was instigated by Howard Rheingold adapting the Corneli and Danoff (2011) work on Paragogy, their word for conscious practice of peer learning, along a less academic paper, more practical, DIY tract convened a group of us including Bryan Alexander, Paul Allison, R\'egis Barondeau, Doug Breitbart, Suz Burroughs, Jay Cross, Julian Elve, Mar\'ia Fernanda, James Folkestad, Kathy Gill, Gigi Johnson, Anna Keune, Roland Legrand, Christopher Neal, Ted Newcomb, Stephanie Parker, Charlotte Pierce, David Preston, Paola Ricaurte, Stephanie Schipper, Fabrizio Terzi, and Geoff Walker together with the goal of producing a handbook explaining how other peers could learn effectively with other peers on a given project. Producing the book itself was our self-fulfilling method of researching our ideas about peer learning.

\subsection{What did we learn in 2012?}

In the Peeragogy project, we've identified several basic and more elaborated patterns that describe these effects. The central pattern is that of a Roadmap, which can apply at the individual level (as a personal learning plan) or at a project level. The roadmap might include a ``reason why'', thoughts about the goal, indicators of progress, a section for future work, and so forth. Group culture around maintaining and updating the roadmap define project governance. Other patterns flesh out the project's emergent properties as a sort of ``agora'':

Convene:

    Focusing on a Specific Project - Lightbulb moment: Most specific projects involve learning!

    Creating a Guide - Overviews expose the lay of the land. Collecting content and stories.

Organize:

    Roles - Specialize and mix it up. Play to participants strengths and skills.

    Newcomer - Create a guide for ``beginner's mind'' and help avoid need to introduce new members each ``meeting.''

    Wrapper - Consolidate and contain. Front end appearance to participants.

Cooperate:

    Heartbeat - The ``heartbeat'' of the group keeps energy flowing.

    Carrying Capacity - Know your limits, find ways to get other people involved.

    Moderation - When leaders step back, dynamics can improve; moderator serves as champion and editor.

    Polling for Ideas - Invite brainstorming, collecting ideas, questions, and solutions.

    Patient - Do not hold grudges and do not make pithy comments about team members or other institutions.

    Sacrifice - Participants must be willing to sacrficice credit often.

Belief:

    Without this the project will likely be doomed or require financial reward.

Assess:

    Use or Make? - Repurposing, tinkering, or creating from scratch?

    Discerning a Pattern - Found a pattern? Give it a title and example.


These patterns provide a natural framework for participatory design and research in peer learning projects.

\subsection{Peer Survey}

To illustrate how this can work, we prepared a short survey for Peeragogy project participants. We asked people how they had participated (e.g Signing up for access to the Social Media Classroom and mailing list, Joining the Google+ Community, Authoring articles, etc.), and what goals or interests motivated their participation. We asked them to describe the Peeragogy project itself in terms of its aims and to evaluate its progress over the first year of its existence. As another measure of ``investment'' in the project, we asked, with no strings attached, whether the respondent would consider donating to the Peeragogy project. This survey was circulated to 223 members of the Peeragogy Google+ community (both en masse, and with individual +Name call-outs), as well as to the currently active members of the Peeragogy mailing list.

The outline of the project's purpose ranged from general -- How to make sense of learning

in our complex times -- to much more specific:

Push education further, providing a toolbox and [techniques] to self-learners. In the peeragogy.org introduction page we assume that self-learners are self-motivated, that may be right but the Handbook can also help them to stay motivated, to motivated others and to face obstacles that may erode motivation.

Considering motivation as a key factor, it is interesting to observe how various understandings of the project's aims and its flaws intersected with personal motivations. For example, one respondent (who had only participated by joining the Google+ community) was [Seeking] [i]nformation on how to create and engage communities of interest with a shared aim of learning.

More active participants justified their participation in terms of what they get out of taking an active role, for instance:

Contributing to the project allows me to co-learn, share and co-write ideas with a colourful mix of great minds. Those ideas can be related to many fields, from communication, to technology, to psychology, to sociology, and more.

The most active participants justified their participation in terms of beliefs or a sense of mission:

Currently we are witnessing many efforts to incorporate technology as an important tool for the learning process. However, most of the initiatives are reduced to the technical aspect (apps, tools, social networks) without any theoretical or epistemological framework. Peeragogy is rooted in many theories of cooperation and leads to a deeper level of understanding about the role of technology in the learning process. I am convinced of the social nature of learning, so I participate in the project to learn and find new strategies to learn better with my students.

I wanted to understand how ``peer production'' really works. Could we create a well-articulated system that helps people interested in peer production get their own goals accomplished, and that itself grows and learns? Peer production seems linked to learning and sharing - so I wanted to understand how that works.

They also expressed criticism of the project, implying that they may feel rather powerless to make the changes that would correct course:

Sometimes I wonder whether the project is not too much ``by education specialists for education specialists''. I have the feeling peer learning is happening anyway, and that teens are often amazingly good at it. Do they need ``learning experts'' or ``books by learning experts'' at all? Maybe they are the experts. Or at least, quite a few of them are.

Another respondent was more blunt:

What problems do you feel we are aiming to solve in the Peeragogy project? We seem to not be sure. How much progress did we make in the first year? Some..got stuck in theory.

But, again, it's not entirely clear how the project provides clear pathways for contributors to turn their frustrations into changed behavior or results. Additionally we need to be entirely clear that we are indeed paving new ground with our work. If there are proven peer learning methods out there we have not examined and included in our efforts, we need to find and address them. Peeragogy is not about reinventing the wheel.

It's also not entirely clear whether excited newbies will find pathways to turn their excitement into shared products or process. For example, one respondent (who had only joined the Google+ community) had not yet introduced their fascinating projects publicly:

I joined the Google+ community because I am interested in developing peer to peer environments for my students to learn in. We are moving towards a community-based, place-based program where we partner with community orgs like our history museum for microhistory work, our local watershed community and farmer's markets for local environmental and food issues, etc. I would love for those local efforts working with adult mentors to combine with a peer network of other HS students in some kind of cMOOC or social media network.

\subsection{Survey Analysis}

Clearly, many participants will have intermediate levels of investment -- basically ``social consumers'' of the project as a ``product''. However, if we think about the metaphor of a college or university, this description also applies to most members of the student body, who are physically present only for a brief portion of the institution's history, and who may not join the student government etc. A blueprint for ``Peeragogy.EDU''\footnote{See \url{http://peeragogy.org/knight-foundation-prototype-fund-proposal-unfunded/}} should include plenty of room for people who take a less involved role. Nevertheless, integrating some of these light-weight contributions (like blog posts about the ideas) would be an important role for more active participants to take on.

Some of the big challenges can be parsed out using our high-level patterns. These issues could define new project ``roadmaps'' and ``teams'':

    Cooperate ~ How to build a really strong collaboration?

        A team is not a group of people who work together. A team is a group of people who trust each other...

    Convene ~ How to build a more practical focus?

        The insight that the project will thrive if people are working hard on their individual problems and sharing feedback on the process seems like the key thing going forward. This feels valuable and important.

    Organize ~ How to connect with motivated newcomers?

        I just came on board a month ago. [...] I am designing a self organizing learning environment (SOLE) or PLE/PLN that I hope will help enable communities of life long learners to practice digital literacies.

    Assess ~ How to be effective and relevant?

        I am game to also explore ways to attach it to spaces where funding can flow based on real need in communities.

The basic workflow in the project -- discussing ideas, condensing them into written handbook sections, annotating them with new resources in informal discussion, reevaluating and rewriting -- seems relatively sustainable, as long as we have community members and editors who are willing to do the work. However, the long-term relevance of the project will come from building workflows that are less self-referential and more applied. With the current foundation in theory and examples from literature and day-to-day activities of participants, we are prepared to be a more effective peer-produced accelerator for peer learning and peer production projects. The kinds of critical questions elaborated above would tend to apply to other projects as well.

\subsection{More possible ideas for this section}

Pretty much everyone needs a team.

We can also form a brief survey\footnote{\url{https://docs.google.com/forms/d/1wVFbrLmZG6PNGtJZykbIgxubfTNChAUxbt-LMFpYLmk/viewform}} recycling material from the book, e.g. the stuff from Connie Gersick that Gigi wrote about\footnote{\url{http://peeragogy.org/convene/}} -- or the reference from Ted that we reused later\footnote{\url{http://peeragogy.org/motivation/}}

We can also draw on the answers to our initial round of questions (a ``pilot study'') -- that info is summed up in http://peeragogy.org/organize/

$\rightarrow$ The Why of this document? \ldots Turn theory into physical reality.

$\rightarrow$ How of this document \ldots 90, 1 % rule doesn't apply to peeragogy $\rightarrow$ SMC data http://sinekpartners.typepad.com/refocus/2010/04/the-weirdos.html

$\rightarrow$ Case study of making Peeragogy Handbook (Google+, SMC, Wordpress data) is more than enough for 10 pager

$\rightarrow$ If it's not grounded in theory enough/we don't have enough data/time...

$\rightarrow$

$\rightarrow$ What of this ``''


Fabrizio; Happy to help in LaTex and eventually infographic..

*** John mentioned something about learning/hour metric\ldots can we incorporate something like that into our assessment??

    1 or more example(s) from each would be great!:

        working through the book to find one or two papers per section

        Christopher's Peeragogy Weekly Summaries

        The Forums

        Google+

        SMC Videos \& Chats

        Twitter

    Public Relations?? $\rightarrow$ Who has written about us in the last year?


%
%
% New Section note for visual aid while editing
%
%

\section{2013 Problem - Peeragogy Accelerator}

Having piloted the peeragogy patterns as a research method for understanding the peeragogy project itself, work is now underway to apply them in another peer learning and peer production community, PlanetMath, in the context of evaluating socio-technical change associated with a public beta of new software for the decade-old site.

I would emphasize the transition from ``innovative project'' in ``sustainable learning design'' in short, we've been doing ``peer support'' and ``critical thinking'' all along
Example: Joe and Charlie made a simple peer support pact outside of P2PU ---this led to--$\rightarrow$ papers ---which led to--$\rightarrow$ some of the seeds for the Peeragogy project

we're not just offering content
we're also not offering ``classes'' (or a place to organize classes)
We're working at a higher level, more strategic
We're focusing on people instead of topics/subjects
And I would also say ``Leadership led team skills''

Charlotte
Joe
Charlie
Fabrizio
John
Regis

\subsection{More possible ideas for this section}

Also, how will we use what we learned to make 2013 better? (use
Peeragogical discoveries to improve the Peeragogy Handbook, Project,
spin-off and partner projects, etc.)

As we move into year two and an updated Handbook, we focus on translations and formalizing peeragogical patterns for problem solving; i.e., how can we (and other peers) use our ideas to better solve problems facing us directly.

In the course of this paper we will examine peeragogical applications to an online Math web cornucopia, Chicago based zine and a New England Independent Publishers association. The main problem we in 2013 and here in this paper are trying to solve is seeing if peeragogical patterns of transparency, accountability and efficiency can help us individually with pressing project problems. Specifically we seek to transition from an innovative theoretical project to a sustainable, easily replicable (peer project) problem solving accelerator.

Discussion: Joe will start this by Tuesday

    Statistics drawn from the SMC database => what do they say that's relevant to helping us understand where things are going

        Which statistics should we pull out?

             of posts per person

             of posts over time

             quality rate ?

                Can we understand how changing quality of the handbook relates to participation?

                Can we understand the changing ``feel'' of participation?

        We can also likely pull some similar stats out of Wordpress and potentially G+, although getting comments out of G+ would probably require more work than anyone wants to put in right now

            This would document how the handbook itself ``grew'' over time

            (discussion with R\'egis about this)\footnote{\url{https://plus.google.com/u/0/101437188321463196206/posts/eUxkDqEAmvG}}


%
%
% New Section note for visual aid while editing
%
%

\section{Meta paper section}

This section is optional at this stage

\subsection{Invited co-authors and initial contributions}

    Fabrizio Terzi Y- I'd like to contribute trying to combine and clarify more points in a visual way for ``research paper'' \& ``research presentation'' submissions . [ONE-PAGER]

    Joe Corneli Y - I'd like to contribute to structuring the argument (e.g. mindmapping) and making this into a proper, publishable, research paper (e.g. writing, editing, reference checking). I think it would be useful for me to re-use the ideas here in the ``Discussion'' section of my thesis. [ONE-PAGER]

    R\'egis Barondeau Y- ``Uses and impact of wikis and other open resources, tools, and practices in fields and application areas.'' ** [ONE-PAGER]

    John Graves Can contribute my research into the literature, most of which is listed here. Also, SlideSpeech interactivity has been put into production so delivery of the paper (the presentation of it) could be collaboratively authored in the SlideSpeech system. Here is the SlideSpeech interactivity tutorial: [ONE-PAGER]

    Samuel Rose Y - I am interested in these areas: Innovative development and/or implementation of wiki applications, Building open systems and tools, Open knowledge and information production, Uses and impact of wikis and other open resources, tools, and practices in fields and application areas \ldots and I will commit to coming up with a cohesive contribution that covers at least some of this. [ONE-PAGER]

        R\'egis: Samuel, please check, modify, complete what I started. 

    Charlotte Pierce Y [ONE-PAGER]

    Charlie Danoff Y [ONE-PAGER] Interested in Open Ed, Wikis, Sharing OER, lately been using GitHub to remix and share seconday school syllabi \& lesson plans ... interested in how peeragogical patterns might make my efforts more effective \& efficient

    Paola Ricaurte Y I'm interested in the social and cultural aspects of open collaboration: social and cultural capitals (Bourdieu): language, digital competences, transnational networks, and so on. Is there anyone else interested in these topics? [ONE-PAGER]

    Anna Keune Y [ONE-PAGER]

    Samuel Zwaan 


The general call is here and a more specific call for the ``open collaboration track'' is here. The submission deadline is March 17, 2013. We'll have to choose between a ``research paper'' and a ``research presentation''; the page limit for both formats is 10 pages.

Key issues for us in the call:

Research papers present integrative reviews or original reports of substantive new work: theoretical, empirical, and/or in the design, development and/or deployment of novel concepts, systems, and mechanisms. Research papers will be reviewed by a research track program committee to meet rigorous academic standards of publication. Papers will be reviewed for relevance, conceptual quality, innovation and clarity of presentation.
NB. Our initial notes on this have been copied to another document to help get focused on the submission. The initial version of ``Roadmaps in Peer Learning'' is here.

\subsection{Overview of Contributed Ideas - Invisible College}

If we're imagining a ``virtual college'' that instantiates the new invisible college of distributed networks, we might begin with a familiar image above like this one:

Figure 1. An abstraction of the familiar college campus

Once we understand the virtual versions of these fixtures of the campus, we can start to look for the ``paths in the grass'' -- those emergent patterns that show how people want to use the space. We can then go beyond this picture and ask how it is wrong or misleading, when we consider the nature of technologies like wikis, and the role they can play in coordinating learning and research in a globally-connected environment.

On pp. 4-5 of The New Invisible College, Caroline Wagner introduces ``five forces'' that match a familiar schema. Networks become the laboratory. The circulation of people and ideas gives a new meaning to the forum. Access to the inevitably ``sticky'' features of geography and rare artifacts generalize the library. Distributed teams working in both local communities and with global interconnection provide a space for informal collaboration, socialization, and learning. But the key feature is emergence -- what happens when we put these other features together.

Just starting with the titles or main ideas from the contributed one-page papers for now, please reorder, add detail, and bridges or context as needed -- and move points into the more FORMAL paper outline below. Each of the top-level headings should probably have 3 or 4 main sub-points -- that's a, b, c, d in the format that Google Docs uses :-). Please also refer to the outline of the Peeragogy Handbook 2.0 -- maybe this paper can be a ``warm-up'' for that. We can also draw writing directly from the Handbook 1.1 if we need/want.

        What is the one idea that connects our various contributions and thoughts...? The thread that will connect everything together... the thesis statement, as it were?

    Designs for a distributed university

        New Invisible College: becoming concrete through self-reflection of research on wikis for research (and education): I can provide a short ``book report'' on Wagner's monograph...

        I want to talk about wikis and wiki-like systems as places for capturing the ``externalities'' from other value-creation systems -- a way to document ``the paths in the grass'' that come from unexpected links between different things

        I'm trying to think about ways to do a tiny (10 day) study on PlanetMath along the lines of the themes I just mentioned...

    Creative confrontation for co-leading

        This seems connected to the Forum that in the Notes section that accompanies my write-up -- it also seems that with the various ``contradictory'' ends, the proposal from Fabrizio moves out of the institution of the forum, and into the ``no-man's land'' of OER communities. As such, it gives a nice statement of ``the problem to be solved'' in our research collaboration -- maybe the ``grand challenge''.

    Benefits of wikis in learning

        Stats and charts drawn from the first year of the Peeragogy project in the SMC -- but what stats and charts? What do we want to show or learn about the project from a quantitative point of view? What can we do to connect this to qualitative matters drawn from our own experience with the project?

    An experiment in the efficiency of learning

        Power laws...? Note that the Peeragogy project will also exhibit some power-law like features (no doubt). What can we learn from this? When I think about power laws, I often ask ``what's the exponent?''. What makes the difference between rapid fall off and less-rapid fall off? How does this relate to ``learning''?

    The digital medium is actually going to look nothing like our traditional concept of space

        maybe some notes about the design of SMC2 in light of what we've learned in the Peeragogy Project? 

    Case studies, effective patterns, and potential applications

        PeerPubU - one possible chance to do a ``research intervention'' on March 30...

        or at least to write down some observations :)

        What is our ``contribution to knowledge'' in this paper? (High-level summary of the key findings and ideas.)\cite{paragogy}
\cite{Origins}
\cite{Tales}
\cite{Peeragogy-2}
\cite{College}
\cite{Bridges}
\cite{peer}
\cite{Gluing}
\cite{GroupInformatics}
\cite{Why}
\cite{PeeragogyinAction}

%
%
% New Section note for visual aid while editing
%
%

\section{Conclusion}

    The main point, I think, is, this one: What are the methods we've identified that will help us make progress towards our goals?

                Hypothesis 1 : in a peeragogy environment the 90-9-1 principle doesn't make sense

                Hypothesis 2 : the long tail rule applies - This may validate an other point in the section ``managing participation''

                Hypothesis 3 : most contributors influence the structure of the site not only the content (meaning re-organize the links over time) - I my wiki experience I see often a bunch of architectes create the structure and users follow it

                Hypothesis 4 : peer learning projects need to find the right balance of freedom, interest and bureaucracy

        I had an interesting idea about the power law of participation. The 90/10/1 breaks down when you work with small groups (like 1 person) -- and I'm guessing that the ``long tail'' is much longer (and skinnier) in G+ than in SMC. However, it's not necessarily that fat in SMC either.

        Also, again, ``quality'' seems at least as important as ``quantity''... 

    A ``phenomenological approach'': what is it like to participate or to have participated in the project?


            We can start filling in ideas about these points asynchronously, as Charlie has started below. (Thanks Charlie!)

        The points of the PAR are as follow:

            Review what was supposed to happen

            What happened / is happening?

            What is right or wrong with what we're doing / have done?

            What did we learn or change?

            How can we learn this experience to improve next time?

                Charlie: can we move to using a higher percent of Free Software tools? (more likely our work can be shared, remixed \& properly stored?)

        This aspect of the paper would echo the Paragogy paper that Joe and Charlie presented at OKCon 2011, which would provide a good point of comparison -- have we learned anything since ``our P2PU days''?

What problem are we aiming to solve in these 10 pages, during the
course of our brief collaboration around writing this paper? Part of
the purpose of the paper is to explain the purpose of the project!

In my view, it is probably along the lines of the Wrapper role we
identified early on, summing things up for people who weren't there --
what are the ``highlights''?

``SportsCenter highlights of Peeragogy''

Let's look at that on instant replay.

Could this be useful to programmers at WikiSym as a way for them to crowdsource their documentation?

In order to make the paper a ``research paper'', we have to phrase
this as a ``contribution to knowledge'' - so we will focus on the
question ``what did we learn?''

Charlie: We learned that organized strangers can work asynchronously
with infrequent synchronous meetings to produce a 230+ page [living]
work [that is much richer than what any one of these people could have
  produced alone!].

Joe: \ldots It's not just the length that's impressive, but the
qualitative aspects of the book, and of working on the book. So, for
instance, we could have potentially put together a 230 page version of
our Paragogy book last November, but it might just have been a lot of
free-form blather. By contrast, the Peeragogy book is pretty readable,
coherent, well-referenced, and so on (with room to grow in terms of an industry standard how to handbook).


This paper can be thought of as a moment in time of the Peeragogy Project, sort of like a financial statement (e.g. Balance Sheet) we want to understand where the money/learning's been going over the past year to budget learning for next year

Future steps
Outreach

Bring individuals who have cool projects

Individuals have a lot of motivation, which is great, but they may need some support even if they are ``self-starters''.

``If you want to go fast, go alone, if you want to go far go together.''
We tend to need clear outputs, some form of assessment (e.g. a paper,
a talk, a thesis, a ``masterpiece'')
Exploring what we actually need to do stuff ``like a university'' -- computer programs?... meetings?
Documenting the more distributed knowledge process
e.g. you can watch a talk online

Social Media Classroom data? (sorry if this is somewhere else in the paper)

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
% (Uncomment to reproduce the .bbl file if needed!)

%% \bibliographystyle{abbrv}
%% \bibliography{bib}  % sigproc.bib is the name of the Bibliography in this case

\begin{thebibliography}{10}

\bibitem{Origins}
C.~Alexander.
\newblock The origins of pattern theory, the future of the theory, and the
  generation of a living world,, 1996.

\bibitem{paragogy}
J.~Corneli and C.~J. Danoff.
\newblock Paragogy.
\newblock In S.~Hellmann, P.~Frischmuth, S.~Auer, and D.~Dietrich, editors,
  {\em Proceedings of the 6th Open Knowledge Conference}, Berlin, Germany,
  2011.

\bibitem{PeeragogyinAction}
J.~Corneli, A.~Keune, C.~J. Danoff, and A.~Lyons.
\newblock Peeragogy in action.
\newblock In {\em The Open Book}, pages 80--87. The Finnish Institute in
  London, 2013.

\bibitem{peer}
C.~J. Danoff.
\newblock The {P}aragogical {A}ction {R}eview.
\newblock {\em submitted to African Journal of Information Systems}, pages
  37--65, 2013.

\bibitem{Gluing}
A.~Dougherty.
\newblock {G}luing the {W}eb {T}ogether: {A}n {I}nterview with {L}arry {W}all.
\newblock {\em ZD Internet User}, 1998.

\bibitem{Tales}
R.~P. Gabriel.
\newblock {\em Patterns of Software}.
\newblock Oxford University Press, New York, 1996.

\bibitem{GroupInformatics}
S.~Goggins, C.~Mascaro, and G.~Valetto.
\newblock Group informatics: A methodological approach and ontology for
  understanding socio-technical groups.
\newblock {\em Journal of the American Society for Inforamation Science and
  Technology}, 2013.

\bibitem{Why}
D.~S. Hugo~Mercier.
\newblock Why do humans reason? arguments for an argumentative theory.
\newblock {\em Behavioral and Brain Sciences}, pages 34,57--111, 2011.

\bibitem{Bridges}
D.~McGavran.
\newblock {\em The Bridges of God}.
\newblock World Dominion Press, 1955.

\bibitem{Peeragogy-2}
H.~Rheingold et~al.
\newblock {\em The Peeragogy Handbook version 1.1}.
\newblock Chicago: PubDomEd Press, 2013.

\bibitem{College}
C.~S. Wagner.
\newblock {\em The New Invisible College}.
\newblock The Brookings Institution, Washington D.C., paperback edition
  edition, 2005.

\end{thebibliography}

\end{multicols}

\end{document}
